Data Processing

### 2024-04-08 analysis/documents/1-data-preparation.qmd
fix base map zoom, add loading of data set

saveRDS(anns_wide_noempty, here::here("data", "objects", "annotations_wide_noempty.rds"))
```

@@

map <- ggmap::get_stadiamap(bbox = c(left = -90, bottom = 50, right = -83, top = 55.5), 
                            zoom = 3, maptype = "stamen_terrain")

>>>>

saveRDS(anns_wide_noempty, here::here("data", "objects", "annotations_wide_noempty.rds"))

# anns_wide_noempty <- readRDS(here::here("data", "objects", "annotations_wide_noempty.rds"))
readr::write_csv(anns_wide_noempty, here::here("data", "tabular", "annotations_wide_noempty.csv"))
```

@@

map <- ggmap::get_stadiamap(bbox = c(left = -90, bottom = 50, right = -83, top = 55.5), 
                            zoom = 5, maptype = "stamen_terrain")
